|

### 2024-10-24 output/seminar-slideshow.qmd
Configure graphical output

---
title:     |
  Parámetros multidimensionales en Teoría de Respuesta al Ítem:
  ¡Algo estamos haciendo mal!
author:    |
  <table>
    <tr>
      <td>Daniel Morillo, Ph.D.</td>
    </tr>
    <tr>
      <td>
        <center>
          [![](../www/slideshow-assets/github-logo.png){height="50"}](https://github.com/DaniMori/)&emsp;
          [![](../www/slideshow-assets/orcid.png){height="50"}](https://orcid.org/0000-0003-3021-3878)
        </center>
      </td>
    </tr>
  </table>
institute: |
  <table>
    <tr>
      <td>
        <center>
          [![](../www/slideshow-assets/logos_fac_psicologia.svg){height="120"}](https://www.uned.es/universidad/facultades/psicologia.html)
        </center>
      </td>
    </tr>
  </table>
bibliography:  ../www/Multidimensional-parameters-MCLM.bib
csl:           ../www/apa-old-doi-prefix.csl
date:          "2024-10-21"
date-meta:     "2024-11-27"
date-format:   long
editor:
  mode:        source
  markdown: 
    wrap:      sentence
    canonical: true
lang:          es
knitr:
  opts_knit: 
    root_dir:  here::here()
  opts_chunk: 
    results:   asis
format:
  revealjs:
    auto-stretch:            true
    code-annotations:        hover
    df-print:                paged
    fig-cap-location:        bottom
    incremental:             false
    keep-md:                 true
    link-external-newwindow: true
    self-contained:          true
    slide-number:            false
    theme:                   ../www/slideshow-assets/extra-styles.scss
    transition:              none
    view-distance:           3
    template-partials:
      - ../www/slideshow-assets/title-slide.html
editor_options: 
  chunk_output_type: console
---

@@

```{r libraries}
#| include: false

library(tibble)
library(dplyr)
library(knitr)
library(tidyr)
library(ggplot2)
library(lavaan)
library(semPlot)
```

```{r souces}
source("../R/Output.R", encoding = 'UTF-8')
```

@@

```{r read-chunks}
read_chunk("../src/Graphical_example_paper.R")
```

```{r constants}
```

```{r graphical-output-conf}
```

>>>>

---
title:     |
  Parámetros multidimensionales en Teoría de Respuesta al Ítem:
  ¡Algo estamos haciendo mal!
author:    |
  <table>
    <tr>
      <td>Daniel Morillo, Ph.D.</td>
    </tr>
    <tr>
      <td>
        <center>
          [![](../www/slideshow-assets/github-logo.png){height="50"}](https://github.com/DaniMori/)&emsp;
          [![](../www/slideshow-assets/orcid.png){height="50"}](https://orcid.org/0000-0003-3021-3878)
        </center>
      </td>
    </tr>
  </table>
institute: |
  <table>
    <tr>
      <td>
        <center>
          [![](../www/slideshow-assets/logos_fac_psicologia.svg){height="120"}](https://www.uned.es/universidad/facultades/psicologia.html)
        </center>
      </td>
    </tr>
  </table>
bibliography:  ../www/Multidimensional-parameters-MCLM.bib
csl:           ../www/apa-old-doi-prefix.csl
date:          "2024-10-21"
date-meta:     "2024-11-27"
date-format:   long
editor:
  mode:        source
  markdown: 
    wrap:      sentence
    canonical: true
lang:          es
knitr:
  # opts_knit: # Does not work, see line 88
  #   root_dir:  here::here()
  opts_chunk: 
    results:   asis
    cache:     true
    autodep:   true
format:
  revealjs:
    auto-stretch:            true
    code-annotations:        hover
    df-print:                paged
    fig-cap-location:        bottom
    fig-format:              svg
    fig-height:              6
    fig-width:               6
    incremental:             false
    keep-md:                 true
    link-external-newwindow: true
    margin:                  0
    self-contained:          true
    slide-number:            false
    theme:                   ../www/slideshow-assets/extra-styles.scss
    transition:              none
    view-distance:           3
    template-partials:
      - ../www/slideshow-assets/title-slide.html
editor_options: 
  chunk_output_type: console
---

@@

```{r libraries}
#| cache:   false
#| include: false

library(tibble)
library(dplyr)
library(knitr)
library(lavaan)
library(semPlot)
library(extrafont)
library(tidyr)
library(ggplot2)
```

```{r setup}
#| cache:   false
#| include: false
opts_knit$set(root.dir = here::here()) # See lines 41-42

# Graphical configuration options:
loadfonts(device = "win") # Load fonts (if necessary)
par(family = "Arial", adj = 0.5) # Set graphical device params

margins <- c(12, 1.3, 8, 1.3) # margins for the sem path plots
```

@@

```{r read-chunks}
#| cache: false
read_chunk("src/Graphical_example_paper.R")
```

```{r sources}
#| cache: false
```

```{r constants}
#| cache: false
```

```{r replace-plot-params}
GRAPH_FONT   <- "Arial" # Replace default font to comply with UNED identity
FONT_SIZE    <- 24      # Replace default font size for slideshow
AXIS_LAB_POS <-   .5    # Replace default axis label position for slideshow
LINE_WIDTH   <-   .75   # Replace default line width for slideshow
```

```{r graphical-output-conf}
#| cache: false
```
